On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-02-03 docs/mvfits_paper/mvf.tex
about to resub mvrfits

\par This truncated expansion happens to be a polynomial in at most $N$ variables.

@@

  The grey dashed line marks the value of $\kappa$ where $\j{}=0$. Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. (Bottom) Percentage residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. }

@@

\par Despite the apparent universality of of \eqn{eq:mvt}, there are many cases where $K$ must be orders of magnitude greater than 1 in order for $\vec{f}$ to be accurately represented by a multinomial.

@@

Worst, in cases where the underlying dataset is best described by a rational function, no polynomial of the same family describing the numerator and denominator will yield satisfactory results (e.g. the well known ``Runge's phenomenon'' \cite{10.2307/2323093}).

@@

\par However, we note that $\hat{P}$'s depends on $g$.

@@

\par With the conceptual tools in hand, we may proceed to constructing \gmvr{} by first defining its action, $\mathcal{A}_{\gmvr}$.

@@

\par Lastly, \fig{fig:qnm}'s bottom two panels show absolute fractional residual errors of the complex frequency, $\cw\lmn = \omega\lmn + i/\tau\lmn$.

@@

For comparison, the same residual errors are shown in gray for the model presented in Ref.~\cite{Berti:2005ys}.

@@

@@

@@

As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent of the central values.

@@

For comparison, fractional residual error for models in Ref.~\cite{Berti:2014fga} are also shown.

@@

@@

An alternative use strategy is to use either \gmvp{} or \gmvr{} to determine a fitting ansatz for individual cases (e.g. individual \qnm{s}), and then use these results to develop a single ansatz for all cases.
\par \gmvp{} has been applied to the modeling of \qnm{} frequencies. The resulting models have been constrained in the extremal Kerr limit.
The fits presented are of direct use in Ref. \cite{London:2017bcn}, where efficiently evaluable \qnm{} frequencies are required to generate template waveforms for \gw{} searches and parameter estimation.

>>>>

\par \eqn{eq:mvt}'s truncated expansion happens to be a polynomial in at most $N$ variables.

@@

  The grey dashed line marks the value of $\kappa$ where $\j{}=0$. Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. (Bottom) Percentage absolute residual errors for fits of dimensionless \qnm{} frequencies,, $\cw\lmn$ along with select numerical values (colored markers) computed using Leaver's method \cite{Leaver85}. For comparison, residuals using the models in Ref.~\cite{Berti:2005ys} are shown in gray. }

@@

\par Despite the apparent universality of \eqn{eq:mvt}, there are many cases where $K$ must be orders of magnitude greater than 1 in order for $\vec{f}$ to be accurately represented by a low order multinomial.

@@

Worst, in cases where the underlying dataset is best described by a rational function, no polynomial of the same family describing the numerator and denominator will yield satisfactory results in low order (e.g. the well known ``Runge's phenomenon'' \cite{10.2307/2323093}).

@@

\par However, we note that $\hat{P}$ depends nontrivially on $g$, and is therefore susceptible to noise in the training data.

@@

\par With these conceptual tools in hand, we may proceed to constructing \gmvr{} by first defining its action, $\mathcal{A}_{\gmvr}$.

@@

\par \fig{fig:qnm}'s bottom two panels show absolute fractional residual errors of the complex frequency, $\cw\lmn = \omega\lmn + i/\tau\lmn$.

@@

For comparison, the same residual errors are shown in gray for the model presented in Ref.~\cite{Berti:2005ys};
here, the sharp feature near $\jf=0$ results from their modeling counter and co-rotating \qnm{} as two different curves.

@@

A \texttt{Python} implementation of \eqns{eq:cw_fit_1}{eq:cw_fit_9} is available in Ref.~\cite{lionel_london_2018_1402516} via \texttt{positive.physics.cw181003550}.

@@

A \texttt{Python} implementation of \eqns{eq:ys22220}{eq:ys55550} is available in Ref.~\cite{lionel_london_2018_1402516} via \texttt{positive.physics.ysprod181003550}.

@@

As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent of the central values, and largely result from the model asatz.

@@

For comparison, fractional residual errors for models in Ref.~\cite{Berti:2014fga} are also shown.

@@

An alternative use-strategy is to use either \gmvp{} or \gmvr{} to determine a fitting ansatz for individual cases (e.g. individual \qnm{s}), and then use these results to develop a single ansatz for all cases.
\par \gmvp{} has been applied to the modeling of \qnm{} frequencies. The resulting models have been constrained in the extremal Kerr limit, and perform well compared to similar fits in the literature.
The fits presented here are of direct use in Ref. \cite{London:2017bcn}, where efficiently evaluable \qnm{} frequencies are required to generate template waveforms for \gw{} searches and parameter estimation.

@@
